### 2016-01-26 AcademicPaperSummaries/PaperSummaries.tex
Beeminder test- no changes made
Finished week three, added Basque paper in week 5

\underline{Research question and research area:} This is primarily a methodological paper- Drakos and Gofas are concerned with underreporting bias over terror attacks, leading to the situation in which the count of attacks that we see in news is lower than full sample of terrorist attacks and systematically underrepresents attacks in autocracies without a free press. This paper also speaks to the democracy and terrorism literature, which is where they primarily orient their literature review.
\underline{Construction of terrorism:} Terrorism is violence, or threat of violence calculated to create an atmosphere of fear and alarm. [Observe that this allows for states to perpetuate terrorism, which might be particularly systematically underreported.] 
\underline{Summary of argument and mechanism:} Argue that bias depends on degree of press freedom in country, so less freedom means underpresentation in aggregate databases like the GTD and findings that democracies attract more terrorism. Argue that cannot just put in a control for press freedom in part because it is a component of Polity.
\underline{Data \& methods:} Use concept of ``thinning'' in which count-data is generated as the true number of events weighted by some country-specific probability of inclusion. Assume that policy is ``fundamental determinant'' of underreporting bias because of inclusion of press freedom. Data sample is country-year unit for 153 countries from 1985-1998. Data from MIPT and Rand. Determine underreporting by looking at differences between two linear models (pg 732 of article).
\underline{Findings:} Find evidence that they claim is strongly indicative of underreporting bias in many countries, but they avoid making country-specific observations.
\underline{Notes on related papers:} Wonder if one could use Bayesian techniques to extend this approach, for example, by saying that the posterior would be underreporting $|$ observed attacks.

>>>>

\underline{Research question and research area:} This is primarily a methodological paper- Drakos and Gofas are concerned with underreporting bias over terror attacks, leading to the situation in which the count of attacks that we see in news is lower than full sample of terrorist attacks and systematically underrepresents attacks in autocracies without a free press. This paper also speaks to the democracy and terrorism literature, which is where they primarily orient their literature review.
\underline{Construction of terrorism:} Terrorism is violence, or threat of violence calculated to create an atmosphere of fear and alarm. [Observe that this allows for states to perpetuate terrorism, which might be particularly systematically underreported.] 
\underline{Summary of argument and mechanism:} Argue that bias depends on degree of press freedom in country, so less freedom means underpresentation in aggregate databases like the GTD and findings that democracies attract more terrorism. Argue that cannot just put in a control for press freedom in part because it is a component of Polity.
\underline{Data \& methods:} Use concept of ``thinning'' in which count-data is generated as the true number of events weighted by some country-specific probability of inclusion. Assume that policy is ``fundamental determinant'' of underreporting bias because of inclusion of press freedom. Data sample is country-year unit for 153 countries from 1985-1998. Data from MIPT and Rand. Determine underreporting by looking at differences between two linear models (pg 732 of article).
\underline{Findings:} Find evidence that they claim is strongly indicative of underreporting bias in many countries, but they avoid making country-specific observations.
\underline{Notes on related papers:} Wonder if one could use Bayesian techniques to extend this approach

\textbf{Krueger, Alan B. and David Laitin. 2008. “Kto Kogo?: A Cross-Country Study of the Origins and Targets of Terrorism.” In Terrorism and Economic Development, ed. Philip Keefer and Nor- man Loayza. New York: Cambridge University Press.}

\underline{Keywords:} quant; theory testing

\underline{Research question and research area}\\  Krueger and Laitin write as part of the debate about whether macroeconomic conditions (\textit{e.g.} poverty) motivate people to commit terrorism. 
\underline{Construction of terrorism:} US State department definition: premeditated, politically motivated violence perpetrated against non-combattant targets by subnational groups or clandestine agents, usually intended to influence a target audience. [Observe: no implication of lethality in this definition, and the definition is squishy about the degree of messaging intended.  Unclear, for example, how this classification would handle Hezbollah in Syria.]
\underline{Summary of argument and mechanism}\\ There isn't really a unique theoretical argument here- Kruger and Laitin are trying to test existing competing predictions about whether poverty facilitates terror recruitment.
\underline{Data \& methods}\\ Used State department data on 781 ``significant'' international terror attacks for the first database and 236 suicide attacks from Pape and International Policy Institute for Counter-Terrorism (ICT) for the second databases, with independent variables about the perpetrator (if country of origin and target are the same, suicide attack, multiple attacks) and environment (GDP, terrain, religious affiliation, literacy). Unit of analysis is terrorist attack. Note that any victims that were from a country other than the one that the attack happened in registered as an international attack. Modeling is done via a cross-tab (for differences in sender-receiver) and a negative binomial regression model.
\underline{Findings}\\ Perpetrators of international terrorism tend to hit targets that are closer to the attacker's home base; countries with high civil liberties are less likely to be countries of origin while low income and low-growth countries are more likely to generate attackers

%\underline{Possible extensions} Would be really interesting to take this framework-- in particular origin of attacker less likely the greater the domestic civil liberties are--- and apply it to foreign fighter flows. The mechanism that one might use to assume that the findings might be different could be that more civil liberties means more circulation of ideological propaganda, which triggers more recruitment.

\underline{Notes on related papers}\\ (From in-class summary) They find that the countries of lower GDP are more likely to experience terror activity, which gets close to being the opposite trend argued in the democracy-attracts-terrorism literature.

PE of Terrorism week 5:\\

\textbf{Abadie, Alberto and Javier Gardeazabal. 2003. “The Economic Costs of Conflict: A Case
Study of the Basque Country.” American Economic Review 93(1):113-132.}

\underline{Keywords:} quant; methodology

\underline{Research question and research area} \\ Attempt to quantify the economic costs of terrorism by comparing the actual GDP of Basque Country with a simulated counter-factual GDP of the same region without attacks. 
\underline{Summary of argument and mechanism}\\  This is pretty a-theoretical. They take as a given that ETA terror activity did influence the Basque County's GDP relative to the rest of Spain and then try to quantify what the difference was.
\underline{Data \& methods} Use data from other Spanish provinces that looks like 1960-era Basque to generate a weighted composite counterfactual. Weights selected so that the counterfactual ``Basque'' (going to call ``Basque-C'' from now on) was most similar to real-Basque. Evolve the provinces differently after 1975, when they say that ETA terrorism becomes ``a large-scale phenomenon'' Also use the 1998-199 truce as a experiment for how investment and economic activity changes after truce.\\
\underline{Findings} GDP in the real-Basque country declined about 10\% relative to the ``Basque-C'' control.  The real benefit from this paper would be if you want a template for other such simulation projects.\\
\underline{Notes on related papers} Interesting that we haven't really seen a ton of papers with a close focus on ETA. Maybe a gap in the literature. \\

\textbf{Abrahms, Max. 2012. The Political E↵ectiveness of Terrorism Revisited. Comparative Political
Studies 45(3): 366-393.}
